Manuscript Assignment = Calcasieu

### 2025-04-18 Manuscript_Assignment.qmd
c

Overlap
```{r yearly comparisons - plot}
#| echo: FALSE
d = df_ov |> 
  filter(ychange == 1)

@@

Centroid Distance
```{r yearly comparisons - plot2}
#| echo: FALSE

@@

LSR

@@

```
![Pairwise Niche Overlap Table](images/niche_overlap_table.png)

>>>>

```{r yearly comparisons - plot}
#| echo: FALSE
d = df_ov |> 
  filter(ychange == 1)

@@

```{r yearly comparisons - plot2}
#| echo: FALSE

@@

## LSR

@@

![Pairwise Niche Overlap Table](images/niche_overlap_table.png)
